Verifying Demonstrations

### 2019-04-10 paper/formalization.tex
Adds initial work on formalizing and proving the protocol

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}%
\label{Protocol}

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key%
%, more specifically, an anonymous 
%identity credential that provides unlinkability between contexts but 
%linkability for reuse within the same context
%\sonja{this is actually achieved by our use of prfs for pid and wid,
%not inherent in the credential}
% \footnote{%
%   Given any \ac{CA} that prevents Sybil 
%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
%   be used to make sure that for each identity one-and-only-one
%   cryptographic key is issued.
%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
%   to one's identity.
% }
. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

The core of the \CROCUS protocol consists of generating participation
proofs (joining a protest, participating in witnessing, submitting
proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
verification of that count (in \cref{ProtocolVerification}).

% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
% join, participation, submission (all in in \cref{ProtocolDuring}) and
% verification (in \cref{ProtocolVerification}).

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

After the protest, anyone can count the number of participants (of the protest and the
protocol) and verify anyone else's count given the relevant meta data
(which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

\subsection{Prerequisite: anonymous credentials}%
\label{ProtocolSetup}

Before Alice can have her participation in any event counted by
\CROCUS, she needs to get an anonymous credential and corresponding
keys. This only needs to be repeated when the credential expires or is
lost, in analogy to a passport in terms of expected intervals. The
keys can be reused for an arbitrary number of protests or, given
careful choices in the PRF used for deriving identifiers, other
services that work with anonymous credentials.

We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
getting anonymous credentials, adapting only the notation to fit ours. 
%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key~\((k, 
  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

@@

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.
The goal of \CROCUS is to generate and collect privacy-preserving
participation proofs that can be counted and verified. These proofs
consist of proof shares that are constructed as depicted in
\cref{fig:ProofFig}. The protocol phases are given in
\cref{fig:ProtocolOverview} and described below.

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
    protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text, in
practice at minimum a name.
The organizer then distributes this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest uses the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).

>>>>

\section{Formalization}

\subsection{Setup}

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
Generates a service public--private key-pair~\((\spk, \ssk)\).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
An interactive protocol which returns the secret key~\(\sk\) of the 
participant~\(P\).

@@

\emph{Creation of a protest: \(\cid\gets \GenProtest[s]\).}
Takes a string~\(s\in\{0,1\}^*\) describing the protest cause and returns a 
unique cause identifier~\(\cid\).

\emph{Joining: \((\pid, t_s)\gets \CROCUSjoin[_P][\cid]\).}
Takes the cause identifier~\(\cid\) of a protest and returns the protester' 
protest-specific identifier~\(\pid\) along with a time-stamp~\(t_s\).

A protester who wants to join the protest uses the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
%the algorithms)%
.
The protester also fetches a time-correlated random value, \(t_s\), from 
\(\TS\), \(t_s\gets \TSget\).
